%-------------------------
% Resume in Latex
% Author: Anchor Hu
% Based off of: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage{xcolor}
\usepackage{fontawesome5}
\definecolor{myBlue}{RGB}{0,123,255}
\newcommand{\link}[1]{\color{myBlue}{#1}}
\newcommand{\skill}[1]{\small{\textnormal{$|$ {#1}}}}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
% \addtolength{\topmargin}{-.5in}
\addtolength{\topmargin}{-.6in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      % \textit{\small#3} & \textit{\small #4} \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

% \newcommand{\resumeProjectHeading}[2]{
%     \item
%     \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
%       \small#1 & #2 \\
%     \end{tabular*}\vspace{-7pt}
% }
\newcommand{\resumeProjectHeading}[3]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      % \small#1 & #2 \\
      \textbf{#1} \\
      \small#2 & \small #3 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
  \textbf{\Huge \scshape Zhuo Hu (Anchor)} \\ \vspace{1pt}
  \small \faMobile \ \ +1 (206) 931-2828 $|$ \href{mailto:uwzhuohu@uw.edu}{\faEnvelope \ \ \link{uwzhuohu@uw.edu}} $|$
  \href{https://linkedin.com/in/zhuo-hu}{\faLinkedin \ \ \link{LinkedIn}} $|$
  \href{https://github.com/Anchor-ZhuoHU}{\faGithub \ \ \link{GitHub}} $|$
  \faBuilding \ \ Seattle, WA
\end{center}


%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart

\resumeSubheading
{University of Washington (GPA: 3.8/4.0)}{Seattle, WA}
{Master of Science, \href{https://www.ece.uw.edu/}{\link{Electrical and Computer Engineering}}}{Sep. 2023 -- June 2025}

\resumeSubheading
{University of Nottingham (GPA: 3.78/4.00)}{Nottingham, UK}
{Bachelor of Science with Honours, \href{https://www.nottingham.ac.uk/mathematics/}{\link{Mathematics with Applied Mathematics}}, the First Class}{Sep. 2019 -- June 2023}

\resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
% \section{Technical Skills}

%  \begin{itemize}[leftmargin=0.15in, label={}]
%     \small{\item{
%      \textbf{Programming with Libraries \& Frameworks}{: 
%      \begin{itemize}
%          \item \faJava \quad Spring, Maven, JDBC, JUnit 5
%          \item \faJs \quad TypeScript, Node.js, React, Express
%          \item \faPython \quad PyTorch, pandas, Matplotlib, Plotly, Flask, Optuna
%          \item \textbf{Others} \quad Git, Shell, Docker, PostgreSQL, MySQL, Scheme, R, MATLAB, \LaTeX
%      \end{itemize}
%      }

%      \textbf{Platform}{: IntelliJ IDEA, Visual Studio Code, macOS, Linux, Windows, Google Colab, Amazon Web Services}
%     }}

% \end{itemize}
\section{Programming Skills}

\resumeSubHeadingListStart
\setlength\itemsep{0em}
\item \textbf{Programming Languages:} Java, C/C++, Python, JavaScript (TypeScript), SQL, R, \LaTeX
\item \textbf{Web Development:} React.js, Node.js, Express.js, Flask, Spring, HTML, CSS
\item \textbf{Database Management:} JDBC, MongoDB, PostgreSQL, MySQL
\item \textbf{Platform \& Tools:} Git, Linux, Amazon Web Services (AWS), Docker, Maven
\item \textbf{ML Frameworks:} PyTorch, NumPy, pandas, Matplotlib, Plotly, Optuna, OpenCV
\vspace{-8pt}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Software Engineer (Remote, Part-Time) \skill{React.js, Express.js, MongoDB, AWS, Docker}}{Seattle, WA}
{Ningbo ResChain Supply Chain Technology Co., LTD. (Startup)}{Sep. 2023 -- Present}

\resumeItemListStart
\resumeItem{Self-engineered a full-stack application, {\link{iShipment}}, for the startup forwarder enterprise as a co-founder.}
\resumeItem{Developed iShipment as a subset of traditional SaaS systems provided by outsourcing companies, it utilizes the React.js framework, Express.js server, MongoDB database, and AWS deployment. iShipment economizes ResChain $29\%$ annually to bring outsourcing $0$ expenses as a startup. It is tailored to retain only the essential features needed by ResChain, minimizing usage complexity for business members, and operates under ResChain's direct control to ensure the integrity and confidentiality of customer resources, safeguarding against potential leaks and unauthorized access.}
\resumeItemListEnd

\resumeSubheading
{Software Development Intern \skill{Flask, PyTorch, Optuna, Express.js, PostgreSQL, Docker}}{Ningbo, China}
{\href{https://scale.mit.edu/centers/ningbo-china-institute-supply-chain-innovation}{\link{MIT Global SCALE Network}}}{May 2023 -- Sep. 2023}

\resumeItemListStart
\resumeItem{Developed a back-end server using Flask, coupled with an Express.js intermediary adapter, to efficiently connect with the client's (\href{https://www.jusdausa.com/}{\link{Jusda}}) PostgreSQL database and Express.js front-end server. This architecture ensured seamless data integration and optimized performance so that the system response prediction was within 3 ms, all while preserving the client's established system framework.}
\resumeItem{Designed a Neural Network with the professor team for the client to predict the vessel's ETA based on the raw shipments' GPS data given by them. The deliverable model's RMSE reached $7.93$ and adjusted $R^2$ reached $0.93$ by Optuna hyperparameter optimization, for the trajectory between the USWC and Eastern China, the client can predict within half a day's error.}
\resumeItem{Communicated between the client and the non-Chinese speaker professor team as a technical communicator to overcome technical barriers between both business-side teams.}
\resumeItemListEnd

\resumeSubheading
{Research Assistant (Remote) \skill{PyTorch, pandas, Matplotlib, Plotly, MATLAB}}{Nottingham, UK}
{\href{https://minghsiehece.usc.edu/}{\link{University of Southern California}}}{May 2022 -- Sep. 2022}
\resumeItemListStart
\resumeItem{Contributed to developing a robust deep learning algorithm outperforming traditional algorithms as a partial algorithm designer in an academic team with dozens of members supervised by \href{https://minghsiehece.usc.edu/directory/faculty/profile/?lname=Bogdan&fname=Paul}{\link{Professor Paul Bogdan}}. The whole algorithm was tailored to analyze senile dementia patients' data from a California public hospital, and it leverages cutting-edge software engineering techniques and data-driven methodologies to optimize predictive accuracy and healthcare outcomes.}
\resumeItemListEnd

\resumeSubheading
{Data Center Intern \skill{React.js, Express.js, R, MySQL, Python}}{Xinyu, China}
{\href{http://www.sgcc.com.cn/html/sgcc_en/index.shtml}{\link{State Grid Corporation of China}}}{May 2021 -- Sep. 2021}
\resumeItemListStart
\resumeItem{Implementing a revolutionized React.js framework that allows around $90\%$ of team members to transform from stale workflow to input new data in the front-end directly. The new solution will concatenate and organize the database at an Express.js back-end, then use MySQL to retrieve data for presenting basic required statistics and statistical graphs by R. This approach shrunk down over $25\%$ of trivial working time.}
\resumeItemListEnd
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------


\resumeSubHeadingListEnd


% %-----------PROJECTS-----------
% \section{Projects}
%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%           {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
%           \resumeItemListStart
%             \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
%             \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
%             \resumeItem{Visualized GitHub data to show collaboration}
%             \resumeItem{Used Celery and Redis for asynchronous tasks}
%           \resumeItemListEnd
%       \resumeProjectHeading
%           {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
%           \resumeItemListStart
%             \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
%             \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
%             \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
%             \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
%           \resumeItemListEnd
%     \resumeSubHeadingListEnd
%-----------PROJECTS-----------
% \section{Projects}
%     \resumeSubHeadingListStart
%       \resumeProjectHeading
%           {\textbf{iShipment Community} $-$ An open-source version of the Shipping System for ResChain.}{Present}

%       \resumeProjectHeading
%           {\textbf{AIHub} $-$ Demo Hub, with API from OpenAI and Hugging Face for experiments and entertainment.}{Nov. 2023}

%       \resumeProjectHeading
%           {\textbf{EmailPoll} $-$ Full-Stack App, perfect for posting surveys in an internal enterprise resource pool.}{June 2023}

%       \resumeProjectHeading
%           {\textbf{Gitlet} $-$ Version-control System, subset of Git, explicit implementation process documented for novices.}{July 2021}
%     \resumeSubHeadingListEnd
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{EmailPoll} \skill{Python, Flask, JavaScript, React.js, PostgreSQL, OAuth, OpenAI}}
{$-$ A Full-Stack App, perfect for posting surveys in an internal enterprise resource pool.}
{Aug. 2023}
\resumeItemListStart
\resumeItem{Used Flask to serve cross-platform APIs and React.js front-end with GitHub OAuth for abuse prevention.}
\resumeItem{Included unsubscribing method, visualization trends for bi-sides, and images-text interchanging model features.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{Gitlet} \skill{Java, Maven}}
{$-$ An object-oriented version-control system, which mimics a subset of Git with Java.}
{July 2022}
\resumeItemListStart
\resumeItem{Applied Directed Acyclic Graph (DAG) to construct references for parent commits, each commit is implemented by blob to save the different versions and named from each's SHA-1 hash.}
\resumeItem{Implemented mapping from names to blobs by directory structures.}
\resumeItemListEnd
\resumeSubHeadingListEnd


%

%-------------------------------------------
\end{document}
